Details matter: Similar-looking host galaxies can produce different merging compact binary populations

### 2015-04-21 paper/paper.tex
Draft minor changes on action items

Binary evolution calculations suggest the detection rate depends sensitively on the assumed metallicity, in conjuction
with other parameters \citep[see,\,e.g.][and references
  therein]{popsyn-LowMetallicityImpact-Chris2008,popsyn-LIGO-SFR-2008}.\editremark{New dominik et al}
% POINT: 
%   - final BH spin, mass can change number favored
%   - of course
The detected population of compact binary mergers can further favor low-metallicity environments, e.g. through the total
mass of merging binaries.
% POINT: Simple model to encompass all
To explore plausible binary detection scenarios, we adopt a parameterized formalism for binary evolution and event detection, motivated by
the detailed studies of  \abbrvPSgrb{} and \abbrvPSellipticals.  Specifically, we encapsulate all information about
 binary evolution into two  parameterized response functions.  The funciton ${\cal G}(t| Z) =
dN/dt dM_*$ describes how many mergers per unit initial mass occur after a time $t$ since a starburst,
given ambient metallicity $Z$.  The function $p(m_1,m_2|Z)$ is a metallicity-dependent mass distribution for binaries
formed in a metallicity $Z$.
%
Finally, we account for the substantially increased sensitivity of gravitational wave detectors to binaries of larger
chirp mass $\mc=(m_1 m_2)^{3/5}/(m_1+m_2)^{1/5}$; see \abbrvPSellipticals.
%
In terms of this response function, we can therefore calculate the relative contribution to the LIGO  event rate $r_D$
due to any individual galaxy via the following formula 
\begin{widetext}
\begin{subequations}
\label{eq:RatePerGalaxy}
\begin{eqnarray}
r_D  &\equiv& \int^{0}_{-T_{univ}} dt' d\log Z  \, [\dot{M}_*(t') p(\log Z|t) ] \times \; {\cal G}(0-t' | Z)  p(\mc|Z) (\mc/1.2 M_\odot)^{15/6}
%\\
%% {\cal R}(z)&\equiv &  \int dx {\cal R} p(z)
\end{eqnarray}
\end{subequations}
\end{widetext}
In this expression, the galactic star formation rate
$\dot{M}_*$ and star formation metallicity distribution $p(\log Z|t)$ are galaxy-dependent and drawn from our
simulations.

@@

@@

>>>>

Binary evolution calculations suggest the detection rate depends sensitively on the assumed metallicity, in conjuction
with other parameters \citep[see,\,e.g.][and references
  therein]{popsyn-LowMetallicityImpact-Chris2008,popsyn-LIGO-SFR-2008}.\editremark{New dominik et al}
% POINT: 
%   - final BH spin, mass can change number favored
%   - of course
The detected population of compact binary mergers can further favor low-metallicity environments, e.g. through the total
mass of merging binaries.
% POINT: Simple model to encompass all
To explore plausible binary detection scenarios, we adopt a parameterized formalism for binary evolution and event detection, motivated by
the detailed studies of  \abbrvPSgrb{} and \abbrvPSellipticals.  Specifically, we encapsulate all information about
 binary evolution into two  parameterized response functions.  The funciton ${\cal G}(t| Z) =
dN/dt dM_*$ describes how many mergers per unit initial mass occur after a time $t$ since a starburst,
given ambient metallicity $Z$.  The function $p(m_1,m_2|Z)$ is a metallicity-dependent mass distribution for binaries
formed in a metallicity $Z$.
%
Finally, we account for the substantially increased sensitivity of gravitational wave detectors to binaries of larger
chirp mass $\mc=(m_1 m_2)^{3/5}/(m_1+m_2)^{1/5}$; see \abbrvPSellipticals.
%
In terms of this response function, we can therefore calculate the relative contribution to the LIGO  event rate $r_D$
due to any individual galaxy via the following formula 
\begin{widetext}
\begin{subequations}
\label{eq:RatePerGalaxy}
\begin{eqnarray}
r_D  &\equiv& \int^{0}_{-T_{univ}} dt' d\log Z  \, [\dot{M}_*(t') p(\log Z|t) ] \times \; {\cal G}(0-t' | Z)  
 [\int d\mc p(\mc|Z) (\mc/1.2 M_\odot)^{15/6}]
%\\
%% {\cal R}(z)&\equiv &  \int dx {\cal R} p(z)
\end{eqnarray}
\end{subequations}
\end{widetext}
In this expression, the galactic star formation rate
$\dot{M}_*$ and star formation metallicity distribution $p(\log Z|t)$ are galaxy-dependent and drawn from our
simulations.   \editremark{rewrite this to be average chirp mass at a given metallicity}

@@

\subsection{Tidal disruption and black hole mass versus metallicity}
At merger, black holes may promptly engulf a companion neutron star \editremark{same papers as for Brandon:Foucart,
  etc}.  Without  a tidal disruption event prior to merger, the prospects for associated electromagnetic counterparts
are severely diminished.  
To quantify this effect

DISCUSSION: could we explain the redshift distribution of short GRBs this way?

@@

\begin{verbatim}
ACTION ITEMS AND STATUS

* Result script looks good (\texttt{sfr\_to\_rate.py}).  Follow instructions

** May want more Z bins to make sure we resolve it. Our differences between predictions are not huge

*** or rewrite script to use numpy on raw star data.  Use 'starmetal.dat': last colum is age.

** Clear that low-Z matters a lot

*

* Do we get to different answers?  Are they different ENOUGH?

** Overall event rate: different by 20\% between two types. Largely similar.
   - plot versus z_exponent.  Is there a trend

** mass-cut-dependent event rate -- will be more sensitive (e.g., if there
  is a hard cutoff on some masses, as having no EM counterpart)
\end{verbatim}
